---
title: "Assignment5"
sidebar: datavis
---

1.  Using sample datasets or own data, create the following charts using only R graphics functions (i.e. without using any other packages). Be sure you customize the chart with your own style/theme (e.g. font, color, pch, etc.)

<!-- -->

a.  Histogram

```{r}
library(ggplot2)

data<-mpg

## a. Histogram.
hist(mpg$hwy, 
     main="Histogram of Highway MPG", 
     col="lightblue", 
     border="darkblue", 
     xlab="Highway MPG", 
     ylab="Frequency", 
     font.main=2, font.lab=4)

```

b.  Barchart
c.  Vertical

```{r}
barplot(table(mpg$class), 
        main="Bar Chart of Car Classes", 
        col="coral", 
        xlab="Car Class", 
        ylab="Frequency", 
        font.main=2)

```

ii. Horizontal

```{r}
barplot(table(mpg$class), 
        main="Horizontal Bar Chart of Car Classes", 
        col="lightgreen", 
        horiz=TRUE, 
        xlab="Frequency", 
        ylab="Car Class", 
        font.main=2)

```

c.  Piechart

```{r}
pie(table(mpg$class), 
    main="Pie Chart of Car Classes", 
    col=rainbow(length(unique(mpg$class))), 
    font.main=2)

```

d.  Boxplot

```{r}
boxplot(hwy ~ class, data=mpg, 
        main="Boxplot of Highway MPG by Car Class", 
        col=c("skyblue", "pink", "lightgreen"), 
        xlab="Car Class", 
        ylab="Highway MPG", 
        border="darkred", 
        font.main=2)

```

e.  Scatterplot

```{r}
plot(mpg$displ, mpg$hwy, 
     main="Scatterplot of Displacement vs Highway MPG", 
     xlab="Displacement (liters)", 
     ylab="Highway MPG", 
     col="blue", 
     pch=16, 
     font.main=2, font.lab=4)

```

2.  Repeat 1 using ggplot2, with your own style

<!-- -->

a.  Histogram

```{r}
ggplot(mpg, aes(x=hwy)) +
  geom_histogram(binwidth=1, fill="lightblue", color="darkblue") +
  ggtitle("Histogram of Highway MPG") +
  theme_minimal() +
  theme(plot.title = element_text(face="bold"))

```

b.  Bar Chart
c.  Vertical

```{r}
ggplot(mpg, aes(x=class)) +
  geom_bar(fill="coral") +
  ggtitle("Bar Chart of Car Classes") +
  theme_minimal() +
  theme(plot.title = element_text(face="bold"))

```

ii. Horizontal

```{r}
ggplot(mpg, aes(x=class)) +
  geom_bar(fill="lightgreen") +
  coord_flip() +
  ggtitle("Horizontal Bar Chart of Car Classes") +
  theme_minimal() +
  theme(plot.title = element_text(face="bold"))

```

c.  Pie Chart

```{r}
ggplot(mpg, aes(x="", fill=class)) +
  geom_bar(width=1) +
  coord_polar(theta="y") +
  ggtitle("Pie Chart of Car Classes") +
  theme_void() +
  theme(plot.title = element_text(face="bold"))

```

d.  Boxplot

```{r}
ggplot(mpg, aes(x=class, y=hwy, fill=class)) +
  geom_boxplot(color="darkred") +
  ggtitle("Boxplot of Highway MPG by Car Class") +
  theme_minimal() +
  theme(plot.title = element_text(face="bold")) +
  scale_fill_manual(values=c("skyblue", "pink", "lightgreen", "yellow", "purple", "orange", "red"))

```

e.  Scatterplot

```{r}
ggplot(mpg, aes(x=displ, y=hwy)) +
  geom_point(color="blue", size=3) +
  ggtitle("Scatterplot of Displacement vs Highway MPG") +
  theme_minimal() +
  theme(plot.title = element_text(face="bold"))

```

3.  Export the charts using different formats such as:

```{r}
# a. pdf
#ggsave("scatterplot.pdf", width=5, height=4)

# b. jpg
#ggsave("scatterplot.jpg", width=5, height=4)

# c. svg
#ggsave("scatterplot.svg", width=5, height=4)

# d. tiff
#ggsave("scatterplot.tiff", width=5, height=4)

# e. bmp
#ggsave("scatterplot.bmp", width=5, height=4)

```
